Survivable Set Connectivity

### 2015-05-11 draft.tex
started modifying the algorithm part

\section{Tree Embeddings}

@@

\subsection{R\"{a}cke's Trees}

@@

\subsection{RoundGKR Black Box}

@@

Now we will combine the ideas of the linear program to approximate the survival set connectivity. We copy the algorithm as it is written in the paper below, although we will separate the algorithm into portions and explain each portion in detail.
\begin{codebox}
\li Set $H \leftarrow \emptyset$
\li Compute linear program SSC-LP and set to zero any $x_e < \dfrac{k}{n^2}$.
\li Let $x' \leftarrow x*\frac{4}{k}$. 
\li Prepare $\mathcal{D}$ be the distribution of Racke tree embeddings for $G$ with $x'$.
\li \For $\tau$ rounds \Do
\li Sample $(T, y, \text{map})$ from $\mathcal{D}$. 
\li \For $q = 0, ..., 2\log n$ \Do
\li \For $v \in V_t$ \Do
\li With probability $\min\{1, \dfrac{4}{2^q}\}$, $q$-mark $v$
\li \If $v$ is $q$-marked \Then
\li Set $y^{v, q}\leftarrow 2^{q+1}y$ and $E^{v,q} \leftarrow \emptyset$.
\li \For $\tau'$ iterations, \Do
\li $E^{v,q} \leftarrow E^{v,q} \cup$ RoundGKR$(T_v, v, y^{v,q})$ \End
\li $H \leftarrow H \cup \text{map}(E^{v,q})$ \End \End \End \End
\li return $H$
\end{codebox}

@@

After running the linear program, we rescale $x$ to $x'$ by $\frac{4}{k}$ to ensure we have a flow of at least $4$ in each pair $(S_i, T_i)$. This flow of $4$ will correspond to a flow of $4$ on the R\"{a}cke trees.

The RoundGKR algorithm is the main tool used for our rounding scheme. RoundGKR guarantees find paths on trees which avoid edges will be found with probability $\Omega(\frac{1}{\log n})$ (this is Lemma~\ref{lem:findpath}) given there is sufficient flow. We repeat this $\tau' = O(\log n)$ times to assure a constant probability.

We can only run RoundGKR on trees. We introduce R\"{a}cke trees specifically for this purpose. We know a flow of $4$ exists between leaves (Lemma~\ref{lem:mapflows}). Each flow path will go up the tree to some ancestor $v$ and then back down to a leaf. One such path might be found when $v$ gets marked. One path will go to $s_i'$ and one to $t_i'$.

Lemma~\ref{lem:findpath} requires us to have a flow of at least $1$ avoinding some edges. If a flow path from $s_i'$ to $t_i'$ goes through ancestor $v$ and carries a flow of value $f$, we can apply the lemma if $f \geq 1$. We scale the capacities by $2^{q+1}$ in order to search for the flow value. We only scale with probabilities $\dfrac{4}{2^q}$ so our costs does not increase by more than $O(\log n)$. Figure~\ref{fig:roundgkronnode} shows how a flow path might be found.

@@

It is straight forward to show that the cost is not too bad.

>>>>

@@

\section{R\"{a}cke's Trees}

@@

\section{The RoundGKR Procedure}

@@

Now we will combine the ideas of the linear program to approximate a solution to Survivable Set Connectivity. We copy the algorithm as it is written in the paper below, although we will separate the algorithm into parts and explain each part in detail.
\begin{codebox}
\li Set $H \leftarrow \emptyset$
\li Compute linear program SSC-LP and set to zero any $x_e < \dfrac{k}{n^2}$.
\li Let $x' \leftarrow x*\frac{4}{k}$. 
\li Prepare $\mathcal{D}$ be the distribution of Racke tree embeddings for $G$ with $x'$.
\li \For $\tau$ rounds \Do
\li Sample $(T, y, \text{map})$ from $\mathcal{D}$. 
\li \For $q = 0, ..., 2\log n$ \Do
\li \For $v \in V_t$ \Do
\li With probability $\min\{1, \dfrac{4}{2^q}\}$, $q$-mark $v$
\li \If $v$ is $q$-marked \Then
\li Set $y^{v, q}\leftarrow 2^{q+1}y$ and $E^{v,q} \leftarrow \emptyset$.
\li \For $\tau'$ iterations, \Do
\li $E^{v,q} \leftarrow E^{v,q} \cup$ RoundGKR$(T_v, v, y^{v,q})$ \End
\li $H \leftarrow H \cup \text{map}(E^{v,q})$ \End \End \End \End
\li return $H$
\end{codebox}

@@

After running the linear program, we rescale $x$ to $x'$ by a $\frac{4}{k}$ factor, which ensures that we have a flow of at least $4$ in each $(S_i, T_i)$. This flow of $4$ will correspond to a flow of $4$ in the R\"{a}cke's trees.

The RoundGKR algorithm is the main tool used for our rounding scheme. RoundGKR finds paths in trees which avoid specific edges with probability $\Omega(\frac{1}{\log n})$ (this is Lemma~\ref{lem:findpath}) given there is sufficient flow. We repeat this $\tau' = O(\log n)$ times to assure a constant probability of finding such paths.

However, we can only run RoundGKR on trees, not general graphs. We introduce the R\"{a}cke's tree embedding specifically for this purpose. We know a flow of $4$ exists between leaves (Lemma~\ref{lem:mapflows}). Each flow path will go up the tree to some ancestor $v$ and then back down to a leaf. One such path might be found when $v$ gets marked. One path will go to $s_i'$ and one to $t_i'$.

Lemma~\ref{lem:findpath} requires us to have a flow of at least $1$ avoiding some edges. If a flow path from $s_i'$ to $t_i'$ goes through ancestor $v$ and carries a flow of value $f$, we can apply the lemma if $f \geq 1$. We scale the capacities by $2^{q+1}$ in order to search for the flow value. We only scale with probabilities $\dfrac{4}{2^q}$ so our costs does not increase by more than $O(\log n)$. Figure~\ref{fig:roundgkronnode} shows how a flow path might be found.

@@

First, we argue that the cost of the solution found by this algorithm is within polylogarithmic factors of the optimum.
